### 2024-03-28 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

::: {.sourceClojure}
```clojure
(defn as-geo [vega-lite-spec]
  (-> vega-lite-spec
      (update :encoding update-keys (fn [k]
                                      (get {:x :latitude
                                            :y :longitude
                                            :x2 :latitude2
                                            :y2 :longitude2}
                                           k k)))
      (assoc :projection {:type :mercator})))
```
:::

>>>>

::: {.sourceClojure}
```clojure
(defn as-geo [vega-lite-spec]
  (-> vega-lite-spec
      (update :encoding update-keys
              #(case %
                 :x :latitude
                 :y :longitude
                 :x2 :latitude2
                 :y2 :longitude2
                 %))
      (assoc :projection {:type :mercator})))
```
:::
